Study of the hadronization of charged pions

### 2017-02-22 1-Answers-Review.tex

This report is organized in 3 sections: lager issues to resolve, questions from the reviewers, and 
typographical corrections.  There may be some repetition between the 3 sections.  The notation 
is P\# for page \#.

{\it The answers from the authors of the note are all presented in italic script 
to allow a clear distinction.} \\

\section{Larger Issues }
1.
Ownership of the pi+ channel.  This was brought up in an email from the committee chair 
(M. Wood).  Before this analysis can move on to round 2 of the review, the ownership issue 
has to be resolved.  The NPWG chair (also M. Wood) has left it up to the eg2 group to 
resolve it.

{\it We are aware of this issue and we started regular meetings between the different 
groups toward the objective of publishing as soon as possible results coherent with
the different analysis performed on this topic (all three pions in particular). This
will eventually translate into an addendum to this note with comparisons between Hayk's 
and this analysis, which will be used to confirm the proper sizing of the systematic errors. 
In a later stage an extra analysis note from Hayk will be submitted
for the extraction of multi-dimensional results on $\pi^+$.} \\

@@

2.
The particle ID and cuts seem to be well understood.  The acceptance correction and 
radiative corrections need to be developed. There is confusion about how the acceptance 
corrections were done (see Section 2 below). The radiative corrections are incomplete as 
reported in the note.  Both corrections need to be well-understood before the committee can 
approve of the analysis.

{\it The text about acceptance has been reviewed in details to be clearer in this new 
version. The section about radiative corrections has been updated with the new method.
We maybe should meet during the next CLAS collaboration meeting (end of March) to clarify 
some of the simpler issues.} \\

@@

7.
P18, Start of section 2.2.5 - I’m not sure I understand the logic in this.  If you have a drift 
chamber problem, it will be manifest in both the solid and liquid target data and the ratio of 
these should be relatively stable.  Why do you not determine run quality by looking at the 
event rate per coulomb of beam current?  For this quantity, a change in the detector 
operation will show up.

{\it You are right, the motivation for this cut is not stated properly. We are looking 
at the ratio because it would affect our result, while ignoring issues that would not
affect our observable. It is important to note that the initial run list was already
cleaned from known detector failures. (The text is corrected in the note.) }

8.
P19, FIg. 14- Hard to tell how much data was discarded. Maybe give a table of means and 
sigmas for each target or show the cuts on the figure are horizontal lines.

{\it The quantity of data removed is difficult to assess, since the problematic runs were
not passed through the final analysis. We were unable to recover the orginal values of the
fits for these specific figures and we 
lack the problematic run which have been deleted. At this stage, it would be rather time
consuming to recover all the data and update the softwares to run on the new machines, so 
we did not produce this figure. If the reviewer think it is necessary to update this 
figure and provide more information about the discarded data let us know, it is time 
consuming but of course possible.}

@@

On the bright side, the slope and behavior appear to be rather well described by the MC
simulation. We feel that a good reproduction of the data is an indication that the 
acceptance correction will behave properly.} \\

13.
P25, I find this discussion quite confusing.   At top you talk about two binnings.  It’s not just 
binning that is changing, right?  You are using different variables.  Then you talk about the 
extracted weight, but that weight is defined with only one of those sets of variables.  You 
also do it for the other set?  Then you an arbitrary weight cut to take care of the problems 
listed in the middle of the page?  Why not just increase the size of the bins in regions where 
you have too few events or large bin migration?  I don’t see how the procedure you use 
does not lead to holes in your data somehow.  And I don’t really understand what you are 
doing with the second weighting factor.  How is this not doing a double correction for 
acceptance, i.e., a double counting?  This whole section needs to be reworked.  I am fairly 
certain that I don’t really understand what you are doing but it leaves me worried that 
something is amiss.  Anyway, that’s not where you want readers to be.

{ \it The section has been reworked to clarify what we are doing. Few points you raised 
are also answered here:

The first set of variables is the one used for the acceptance correction used for results,
while the second set is only used to evaluate the systematic errors. In the 
note, the formulas are generally given only for the first set for simplicity.

The motivation for using such a strange cut based on the product of different unrelated
values is actually directly linked to the problem of inbent 
particles being directed towards the beam pipe. The $\pi^-$ acceptance drops very 
strongly at low $p_\perp^2$ leading to very high weights, however there is no problem of 
bin migration
or low statistics because the generated yield is very high in this region. We found that 
the best way
to keep these bins while discarding bins where the sizze of the weight is less problematic 
but with issues concerning bin migration and statistics was to apply this type of cut.

In term of method, the two
step acceptance correction is hopefully going to be clearer. It is the same as the method used 
in the previous L. El Fassi et al. analysis note. The second step of the procedure is
specifically used to take care of the bins that are removed by the cut on weights. You 
can see in the formula that the weights
of the previously calculated acceptance are used in this step, ensuring that we do not
double correct the data.

@@

17.
P27, Fig. 22 - the right column of plots is not the same as those in Fig. 15.  Why change the 
variables?

{\it Sorry, it is a mistake on our part, there is no reason. TO BE CORRECTED. And
add figures after radiative correction!} \\

18.
P28 - What is Coulolmb Correction applied to? Momentum of charged particles? Could you 
plot effect of this correction on particles? Is it really big enough to be visible within our 
resolutions ?

{\it The Coulomb correction is applied to incoming and outgoing electrons as well as
produced charged pions. Indeed the effect is invisible in most of the phase space as
it is comparable to the resolution of the detector (points overlap completely). The 
effect is small but visible only for very low $z$ pions. It has been implemented 
because it was suggested it might be big, but we now find that it could have been 
neglected at our kinematics.} \\

@@

19.
P30 - 
fig.24 is missing X axis label. You also may consider 2D histogram for better display.

{\it This figure is replaced by others in the new radiative correction section.} \\

@@

21.
P33, Sec. 2.5.1 - list the negligible effects.

{\it The sentence has been revised to list all effects tested. } \\

22.
P34, Fig. 28 - why is the resolution poorer than in Fig. 12?

{\it Resolution is the same, it looks wider because, on this figure, we show the integrated 
result over the 6 sectors.} \\

@@

23.
P34, why do you have a 1\% normalization error in all the multiplicity ratios when you say just 
above that for this particular sample with two particles in the final state the events in the test 
regions dropped to 0.01?  Doesn’t that mean the target contamination normalization error is 
smaller than 1\%?

{\it Multiplicity ratios are a double ratio. The claim is that the semi inclusive part 
is not affected, but the inclusive electron ratio is affected. This is included
as a normalisation error. We revisited slightly the paragraph to make it clearer.} \\

24.
P34, with this technique of comparing results using the two different sets of variables (you 
call it two binnings, but I think that is sort of misleading), you are using the same events.  
Does this not mean you have a statistical contribution to this systematic error?  You say you 
noticed larger systematic errors for the pi- events due to lower acceptance and bigger 
weights.  Might it also be lower statistics and so you have statistical fluctuations contributing 
to the systematic error?  If so, you are sort of double-counting the statistical error and 
inflating the systematic error more than it should be.

{\it This is an interesting question and we might have overlooked this problem. We changed
our method of calculating the statistical errors to avoid the double counting, see
discussion in the 2.3.1. section about the method to calculate the error bars. } \\

### 2017-02-22 AnalysisNote.tex
Answer some comments!
Update the note on RC and Error bars calculations

\documentclass[a4paper,12pt,twoside]{article}
        \usepackage{graphicx,type1cm,eso-pic,color}
        \usepackage{hyperref}
        \usepackage{longtable}
        \usepackage{amsmath,amssymb} 
        \usepackage[latin1]{inputenc}
        \usepackage[OT1]{fontenc}
        \usepackage{setspace}
        \usepackage{epigraph}

@@

@@

\author{
  Rapha\"el \textsc{Dupr\'e} \\ 
  {\it Institut de Physique Nucl\'eaire, Orsay, France} \\
  Lamiaa \textsc{El Fassi} \\ 
  {\it Mississippi State University, Mississippi State,} \\ 
  {\it Mississippi 39762, USA} \\
  Kawtar \textsc{Hafidi} \\ 
  {\it Physics Division, Argonne National Laboratory,} \\ 
  {\it Argonne, Illinois 60439, USA} \\
  William \textsc{Brooks} \\
  {\it Universidad T\'ecnica Federico Santa Mar\'ia,} \\ 
  {\it Valpara\'iso, Chile} 
}

>>>>

\documentclass[a4paper,12pt,twoside]{article}
        \usepackage{graphicx,type1cm,eso-pic,color}
        \usepackage{hyperref}
        \usepackage{longtable}
        \usepackage{amsmath,amssymb} 
        \usepackage[latin1]{inputenc}
        \usepackage[OT1]{fontenc}
        \usepackage{setspace}
        \usepackage{epigraph}
        \usepackage{lineno}

@@

\linenumbers

@@

\author{
  Rapha\"el \textsc{Dupr\'e} \\ 
  {\it Institut de Physique Nucl\'eaire, Orsay, France} \\
  Kawtar \textsc{Hafidi} \\ 
  {\it Physics Division, Argonne National Laboratory,} \\ 
  {\it Argonne, Illinois 60439, USA} \\
  Lamiaa \textsc{El Fassi} \\ 
  {\it Mississippi State University, Mississippi State,} \\ 
  {\it Mississippi 39762, USA} \\
  William \textsc{Brooks}, Ahmed \textsc{El Alaoui}, Hayk \textsc{Hakobyan}, \\
  Taisiya \textsc{Mineeva} \\
  {\it Universidad T\'ecnica Federico Santa Mar\'ia,} \\ 
  {\it Valpara\'iso, Chile} 
}

### 2017-02-22 chap5.tex
Update the note on RC and Error bars calculations

Once the identification is done, the calculation of our two observables and their statistical uncertainties is straightforward. The latter are given by:
\begin{equation}
{\delta \left ( R_A^h \right ) \over R_A^h} = \sqrt{ 1 /N_A^h + 1/ N_A^e +1/N_D^h + 1/N_D^e}
\end{equation}
and
\begin{equation}
\left ( \delta \left ( \Delta \langle P_\perp^2 \rangle \right ) \right )^2 = 
   \left ({\langle P_\perp^4 \rangle - \langle P_\perp^2 \rangle ^2}\right )_A / N_A^h
 + \left ({\langle P_\perp^4 \rangle - \langle P_\perp^2 \rangle ^2}\right )_D / N_D^h.
\end{equation}

@@

@@

\paragraph{Simulation}
\label{sec:simul}

To correct for acceptance effects, we simulated a total of 100 million events 
per target ($^2$H, C, Fe and Pb) using the PYTHIA \cite{Sjostrand:2006za} 
event generator that was slightly modified to include Fermi motion effects. The 
generated events are processed by CLAS softwares (GSIM, GPP and user\_ana) 
to simulate the detector and the reconstruction process in a fashion similar 
to that done with the experimental data.
% TODO GPP factors

@@

\paragraph{Correction of the Data}

The acceptance correction coefficients are defined as the ratio of reconstructed and generated events,

@@

\begin{table}[htbp]
\center
\begin{tabular} {|l|c|c|c|c|}
\hline
 $\nu$ & \xb & $p_\pi$ & $-t$ \\ \hline
 2.20 & 0.12 & 0.25 &-3.50 \\ 
 3.00 & 0.18 & 0.60 &-2.10 \\ 
 3.40 & 0.22 & 1.00 &-1.75 \\ 
 3.75 & 0.27 & 1.45 &-1.50 \\ 
 4.00 & 0.33 & 1.70 &-1.30 \\ 
 4.25 & 0.60 & 2.15 &-1.10 \\ 
      &      & 3.00 &-0.75 \\ 
      &      & 4.25 &-0.00 \\ \hline
\end{tabular}
\quad
\begin{tabular} {|l|c|c|c|c|}
\hline
 $Q^2$ & $\nu$ & $z$ & $-t$ \\ \hline
 1.00 & 2.20 & 0.00 & -3.50 \\
 1.20 & 3.00 & 0.20 & -2.10 \\
 1.40 & 3.40 & 0.40 & -1.75 \\
 1.65 & 3.75 & 0.45 & -1.50 \\
 2.10 & 4.00 & 0.52 & -1.30 \\
 4.00 & 4.25 & 0.62 & -1.10 \\
      &      & 0.80 & -0.75 \\
      &      & 1.00 & -0.00 \\ \hline
\end{tabular}
\caption{Bin limits used for the acceptance correction described in table \ref{tab:AcceptBinning}.}
  \label{tab:AcceptBins}
\end{table}

@@

The large electric charge of our nuclear targets create an electric field that should be taken into account at our energies. Besides the fact that the nuclear electric field accelerates or decelerates the incoming and outgoing charged particles, it has some non trivial effects such as the focusing of low energy particles. Aste {\it et al.}~\cite{Aste:2005wc} showed that these Coulomb effects could be corrected for by using an effective momentum approximation at large momenta ({\it i.e.}, $Q^2>.5$ GeV$^2$). As our kinematics coverage is beyond this limit, we decided to use this approximation on the coulomb correction of our data-sets. According to Aste {\it et al.}, the best effective potential approximation is given by $\bar V= 0.8 V_0$, where $V_0$ is the electrostatic potential at the center of nuclei. The latter is evaluated as $V_0= -3 \alpha_{EM} Z / (2 R)$, where $\alpha_{EM}$ is the fine-structure constant, Z is the proton number, and R is the radius of nuclei. Table 5 contains the used values of $V_0$ and $\bar V$ on different nuclear target's analysis. We must note that this Coulomb correction has been applied to both electrons and charged pions before calculating any kinematical variables.

@@

Despite its lower magnitude compared to the strong force, the 
electromagnetic force may have a non negligible impact on our results. The 
reason is that even a moderate energy photon emission can modify significantly the measured kinematical variables. To correct this effect, several simulation codes exist \cite{Akushevich:2001yp}, however, none of them treat directly the SIDIS production on nuclei. For that reason, a dedicated Monte-Carlo simulation based on existing codes was developed.

\paragraph{Simulation}

The inclusive radiative effects are generated using the RADGEN code 
\cite{Akushevich:1998ft}, which includes Feynman diagrams shown in 
figure~\ref{fig:FDRadCorr}. Using this code one can evaluate the correction 
factors for inclusive measurements as $\delta = \sigma_{obs} / \sigma_{Born}$, where $\sigma_{obs}$ is the measured inclusive cross section, and $\sigma_{Born}$ is the Born cross section. As RADGEN is also a Monte-Carlo generator for photon emissions, it could be used to modify the virtual photon kinematics before the 
hadron production in any DIS generator. This allows the evaluation of the radiative 
effects on semi-inclusive measurements by implementing RADGEN inside the main 
Monte-Carlo event generator.

\begin{figure}[htp]
\centering
\includegraphics[width=12cm] {chap5-fig/RadDiag.png}
\caption {Diagrams taken into account in RADGEN \cite{Akushevich:1998ft}. The 
diagrams b) to e) contribute to the first order calculation of the radiative 
effects on Born cross section (diagram a)).}
\label{fig:FDRadCorr}
\end{figure}

The Monte-Carlo simulation was done using the event generator, GENIE~\cite{Andreopoulos:2009rq}, that describes well electron-nucleus interactions. Indeed, GENIE contains the quasi-elastic scattering\footnote{Elastic 
scattering off a single nucleon on nuclei.}, which is considered as the main channel generating radiative events in the DIS region \cite{Akushevich:2007jc}. This generator includes also hadronic cascades in nuclei, at which pions might be generated in quasi-elastic events. This is an important feature because the quasi-elastic production can not contribute directly to semi-inclusive measurements.

\paragraph{Correction of the Data}

We generated 100 million events with and without radiative effects for each target. The RADGEN code gave us the magnitude of inclusive correction coefficients, however, the comparison between the two data sets allows the extraction of semi-inclusive correction factors.

The ratio of inclusive correction factors, as depicted in figure \ref{fig:RadCorrFac}, is relatively small (couple of percents at most) except for low \xb and high $\nu$. Similarly for the semi-inclusive factors' ratio shown in figure \ref{fig:RadCorrFacSIDIS} as a function of $z$ and \ptp. However, the associated statistical errors are quite large because only a small fraction of the events involved a photon radiation.

\begin{figure}[htbp]
\centering
\includegraphics[width=9cm] {chap5-fig/ElecRadWei_Lead.png}
\caption {Ratios of radiative correction factors, $\delta_\text{Pb}/
\delta_{^2\text{H}}$, as a function of \xb in various $\nu$ bins.}
\label{fig:RadCorrFac}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=9cm] {chap5-fig/RadGenFactors.png}
\caption {Ratios of radiative correction factors, $\delta_\text{Pb}/
\delta_{^2\text{H}}$, as a function of $z$ (top) and \ptp (bottom).}
\label{fig:RadCorrFacSIDIS}
\end{figure}

The semi-inclusive part of the radiative correction turned out to be limited 
in amplitude for the most kinematics, except for high $z$ and \ptp. Thus, we decided to not apply this correction before further studies.

{\color{red} We found a better way to implement the radiative correction,
that is not limited by the used MC technique. We will implement it in
the second version of the note as we do not want to delay the review process because this correction that we already found to be small. Sorry about that.}

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=10cm] {chap5-fig/HallC-Isospin.png}
\caption {Ratios of deuteron over proton for $\pi^+$s (top) and $\pi^-$s (bottom)
as a function of \xb at $z=0.55$ \cite{Asaturyan:2011mq}.}
\label{fig:IsoSpin}
\end{figure}

>>>>

Once the identification is done, the calculation of our two observables and their statistical uncertainties is straightforward. The latter are given by:
\begin{equation}
\label{eq:MRError}
{\delta \left ( R_A^h \right ) \over R_A^h} = \sqrt{ 1 /N_A^h + 1/ N_A^e +1/N_D^h + 1/N_D^e}
\end{equation}
and
\begin{equation}
\label{eq:DPtError}
\left ( \delta \left ( \Delta \langle P_\perp^2 \rangle \right ) \right )^2 = 
   \left ({\langle P_\perp^4 \rangle - \langle P_\perp^2 \rangle ^2}\right )_A / N_A^h
 + \left ({\langle P_\perp^4 \rangle - \langle P_\perp^2 \rangle ^2}\right )_D / N_D^h.
\end{equation}

@@

Following the first round of questions from the analysis review committee, we
reflected about this implementation of error bars and possible overlap with the 
systematic errors
evaluated below. We found first that the correlation between the weights should reduce
the statistical errors. In a given bin the weights associated with each 
targets are always of similar sizes, this correlation will reduce the size of 
error bars. However, we do not see a method to properly take this 
effect fully into account in term of purely statistical error bars. In order
to solve this issue we came back to a point by the committee on the topic of 
systematic error bars (Q 24). There it was noted that some of these effects are
double counted once in the statistical error and once in the systematic. As these
errors are solely due to the acceptance correction, we decided to account them 
only in the systematic error budget. So we reverted statistical errors to equations
\ref{eq:MRError} and \ref{eq:DPtError} and keep the full systematic errors as they
were evaluated before.

@@

\paragraph{Simulation} ~\\
To correct for acceptance effects, we simulated a total of 100 million events 
per target ($^2$H, C, Fe and Pb) using the PYTHIA \cite{Sjostrand:2006za} 
event generator that was slightly modified to include Fermi motion effects. The 
generated events are processed by CLAS softwares (GSIM, GPP and user\_ana) 
to simulate the detector and the reconstruction process in a fashion similar 
to that done with the experimental data.
% TODO GPP factors

@@

\paragraph{Correction of the Data} ~\\
The acceptance correction coefficients are defined as the ratio of reconstructed and generated events,

@@

\begin{table}[htbp]
\center
\begin{tabular} {|c|c|c|c|c|}
\hline
 $\nu$ & \xb & $p_\pi$ & $-t$ \\ \hline
 2.20 & 0.12 & 0.25 &-3.50 \\ 
 3.00 & 0.18 & 0.60 &-2.10 \\ 
 3.40 & 0.22 & 1.00 &-1.75 \\ 
 3.75 & 0.27 & 1.45 &-1.50 \\ 
 4.00 & 0.33 & 1.70 &-1.30 \\ 
 4.25 & 0.60 & 2.15 &-1.10 \\ 
      &      & 3.00 &-0.75 \\ 
      &      & 4.25 &-0.00 \\ \hline
\end{tabular}
\quad
\begin{tabular} {|c|c|c|c|c|}
\hline
 $Q^2$ & $\nu$ & $z$ & $-t$ \\ \hline
 1.00 & 2.20 & 0.00 & -3.50 \\
 1.20 & 3.00 & 0.20 & -2.10 \\
 1.40 & 3.40 & 0.40 & -1.75 \\
 1.65 & 3.75 & 0.45 & -1.50 \\
 2.10 & 4.00 & 0.52 & -1.30 \\
 4.00 & 4.25 & 0.62 & -1.10 \\
      &      & 0.80 & -0.75 \\
      &      & 1.00 & -0.00 \\ \hline
\end{tabular}
\caption{Bin limits used for the acceptance correction described in table \ref{tab:AcceptBinning}.}
  \label{tab:AcceptBins}
\end{table}

@@

The large electric charge of our nuclear targets create an electric field that 
should be taken into account at our energies. Besides the fact that the nuclear 
electric field accelerates or decelerates the incoming and outgoing charged 
particles, it has some non trivial effects such as the focusing of low energy 
particles. Aste {\it et al.}~\cite{Aste:2005wc} showed that these Coulomb 
effects could be corrected for by using an effective momentum approximation at 
large momenta ({\it i.e.}, $Q^2>.5$ GeV$^2$). As our kinematics coverage is 
beyond this limit, we decided to use this approximation on the Coulomb 
correction of our data-sets. According to Aste {\it et al.}, the best effective 
potential approximation is given by $\bar V= 0.8 V_0$, where $V_0$ is the 
electrostatic potential at the center of nuclei. The latter is evaluated as 
$V_0= -3 \alpha_{EM} Z / (2 R)$, where $\alpha_{EM}$ is the fine-structure 
constant, $Z$ is the proton number, and R is the radius of nuclei. Table 
\ref{tab:Coulomb} contains the used values of $V_0$ and $\bar V$ on different 
nuclear target's analysis. The Coulomb correction is applied to both electrons 
and charged pions before calculating the plotted kinematical variables.

@@

The QED diagrams shown in figure \ref{fig:FDRadCorr} contribute to the measurement
of the leptoproduction of hadrons. The diagram (a) is the Born cross section, the
others are radiative contributions that we would like to subtract in order to 
have results more easily interpretable in term of hadronic physics.
This substraction is what we call the radiative correction, as can be seen 
this correction should take care of real photon productions (diagrams b and c)
but also virtual photon exchange (diagram d) and photon self energy (diagram e).
We neglect exchanges of photons with hadrons as they are suppressed due to the 
large mass of hadrons in comparison to electrons. For practical reasons, we also 
limit this correction to leading order as can be seen from the presented diagrams.

\begin{figure}[htp]
\centering
\includegraphics[width=12cm] {chap5-fig/RadDiag.png}
\caption {Diagrams taken into account in the HAPRAD 2 code \cite{Akushevich:2007jc}. The 
diagrams b to e contribute to the first order calculation of the radiative 
effects of the Born cross section represented in diagram a.}
\label{fig:FDRadCorr}
\end{figure}

The radiative correction is not expected to be important in the multiplicity 
ratios due to the double cancellation between the different contributions of 
the ratio. However, its impact on the transverse momentum brodening is more 
difficult to anticipate. We therefore decided to calculate the correction using 
the recent Haprad 2 code \cite{Akushevich:2007jc} with adaptations to include
nuclear effects such as Fermi motion \cite{Osipenko:PC}. This calculation is
using modeled semi-inclusive structure functions (based on former CLAS
data \cite{Akushevich:2007jc}) and modeled exclusive channels from MAID 2003
\cite{Drechsel:1998hk}. This calculation is the state of the art in the matter
as it is an exact calculation in the complete five dimension cross section
and do not use the peaking approximation generally used in previous method.

To apply the radiative correction, we apply a weight to each events in a fashion
similar to the acceptance correction. The HAPRAD 2 code provides 
$\delta = \sigma_{obs} / \sigma_B$ at given kinematics. Table \ref{tab:RCBins} 
shows the binning used to calculate the radiative correction weights.
We chose to make a finer 
binning for the radiative corrections than for acceptance as the computing time 
to calculate weights is more reasonnable (around 1000 days of cpu time).

\begin{table}[htbp]
\center
\begin{tabular} {|c|c|c|c|c|c|c|}
\hline
Bin Nb & $\nu$ & \xb & $p_\pi$ & $-t$ & $\phi$ \\ \hline

 0     & 2.25 & 0.12 & 0.20 & -3.50 &   0.0 \\ 
 1     & 2.45 & 0.15 & 0.35 & -2.10 &  18.0 \\ 
 2     & 2.66 & 0.17 & 0.50 & -1.75 &  36.0 \\ 
 3     & 2.82 & 0.18 & 0.75 & -1.50 &  54.0 \\ 
 4     & 2.96 & 0.19 & 1.00 & -1.30 &  72.0 \\ 
 5     & 3.07 & 0.20 & 1.60 & -1.10 &  90.0 \\ 
 6     & 3.17 & 0.21 & 2.20 & -0.75 & 108.0 \\ 
 7     & 3.27 & 0.22 & 4.25 &  0.00 & 126.0 \\ 
 8     & 3.37 & 0.23 &      &       & 144.0 \\ 
 9     & 3.46 & 0.24 &      &       & 162.0 \\ 
10     & 3.55 & 0.25 &      &       & 180.0 \\ 
11     & 3.64 & 0.26 &      &       &       \\ 
12     & 3.72 & 0.27 &      &       &       \\ 
13     & 3.80 & 0.28 &      &       &       \\ 
14     & 3.87 & 0.30 &      &       &       \\ 
15     & 3.94 & 0.33 &      &       &       \\ 
16     & 4.01 & 0.36 &      &       &       \\ 
17     & 4.07 & 0.39 &      &       &       \\ 
18     & 4.12 & 0.43 &      &       &       \\ 
19     & 4.18 & 0.48 &      &       &       \\ 
20     & 4.25 & 0.56 &      &       &       \\

\hline
\end{tabular}
\caption{Bin limits used for the radiative correction described in section \ref{RadCor}.}
  \label{tab:RCBins}
\end{table}

We show in figure \ref{fig:RCexample} a selected sample of radiative correction factors
($= \delta_{Fe} / \delta_D$) in order to illustrate the expected effect on observables.
In the large majority of the cases the factors are within 5\% of 1, so we do not expect to
see a strong effect on the final results where these will be integrated. This is confirmed 
in figure \ref{} ... In the case of the transverse momentum braodening, the variations
appear to ...

\begin{figure}[tbp]
\centering
\includegraphics[width=7cm] {chap5-fig/ElecRadWei_Iron_2356.png}
\includegraphics[width=7cm] {chap5-fig/ElecRadWei_Iron_3756.png}
\includegraphics[width=7cm] {chap5-fig/ElecRadWei_Iron_7756.png}
\includegraphics[width=7cm] {chap5-fig/ElecRadWei_Iron_10756.png}
\includegraphics[width=7cm] {chap5-fig/ElecRadWei_Iron_11556.png}
\includegraphics[width=7cm] {chap5-fig/ElecRadWei_Iron_18956.png}
\caption {RC factors ($= \delta_{Fe} / \delta_D$) as a function of $\phi$ and 
$-t$ for a selection of bins specified above each figure.}
\label{fig:IsoSpin}
\end{figure}

\begin{figure}[tbp]
\centering
\caption {Preliminary results ..., 
for multiplicity ratios (top) and transverse momentum broadening 
(bottom). Only statistical errors are shown.}
\label{fig:RCPlots}
\end{figure}

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=10cm] {chap5-fig/HallC-Isospin.png}
\caption {}
\label{fig:RCexample}
\end{figure}
